Combining formal and distributional models of predicate semantics

### 2016-03-03 paper/paper.tex
A little work on SFE description
Former-commit-id: 3d025ff526ef20e1c2e19bfdf9eb23eda687a75b
Former-commit-id: 557af611d39c17216e9de7ab5c463a54ed6189ed

>>>>

Subgraph feature extraction (SFE) is a technique introduced by Gardner and
Mitchell~\shortcite{gardner-2015-sfe} for generating feature matrices over node
pairs in a graph with labeled edges.  Given a pair of nodes in a graph, SFE
performs a search to characterize a subgraph around those two nodes, then
extracts various kinds of features from that subgraph, such as the set of edge
sequences that connect the two nodes.  \mattnote{Give an example graph with
features.}  Gardner and Mitchell used these features to perform link
prediction in the graph, using characteristics of the subgraph around two nodes
to determine if an edge of a particular type should exist between those nodes
(when the graph corresponds to a knowledge base like Freebase, this task is
also known as knowledge base completion). Gardner and Mitchell only used these
features to model formal KB relations, however.

We differ from the work done by Gardner and Mitchell in two ways.  First, we
apply these features to models of natural language, instead of formal KB
relations.  There are some non-trivial problems that need to be solved in order
to make this work, which will be discussed in \secref{method}.  Second, Gardner
and Mitchell only considered generating feature matrices over node \emph{pairs}
in a graph, with which one can model binary relations.  The natural language
queries we wish to answer also involve unary predicates, or categories.  We
thus extend SFE to also generate feature matrices over \emph{nodes} in a graph,
an extension that is straightforward and is also discussed in more detail in
\secref{method}.

\subsection{Other related work}

Manaal's retrofitting semantic lexicons, Sebastian Riedel's ``Injecting Logical
Background Knowledge into Embeddings for Relation Extraction'', work on PRA and
KBC more generally\ldots
